### One value per participant and ID

The ANOVA wants a single value per participant and per condition: we make the average.

```{r average}
data_anova <- df %>%
  group_by(GROUP, SUBJ, ID) %>%
  summarise(MT = mean(MT), .groups = "drop")
```

### ANOVA

```{r anova}
anova_res <- ezANOVA(data = data_anova,
                     dv = MT,
                     wid = SUBJ,
                     within = ID,
                     between = GROUP,
                     detailed = FALSE)
anova_res$ANOVA
```

Movement time increased with difficulty, F(1, 48) = 30.78, p < .001. This increase was different between the groups, F(2, 48) = 11.58, p < .001.


## 1.4 Run the linear regression by GROUP

```{r regression}
data_reg <- data_anova %>%
  mutate(ID_num = parse_number(as.character(ID)))

reg_table <- data_reg %>%
  group_by(GROUP) %>%
  group_modify(~ {
    m <- lm(MT ~ ID_num, data = .x)
    tibble(intercept = coef(m)[1], slope = coef(m)[2])
  }) %>%
  mutate(label = sprintf("MT = %.3f + %.3f * ID", intercept, slope))

reg_table
```


## 1.5 Graph for publication

```{r graph}
#| fig-width: 8
#| fig-height: 6
means <- data_reg %>%
  group_by(GROUP, ID_num) %>%
  summarise(MT = mean(MT), .groups = "drop")

eq_pos <- reg_table %>%
  ungroup() %>%
  mutate(x = 1.5, y = 2.7 - 0.3 * row_number())

p <- ggplot(means, aes(x = ID_num, y = MT, colour = GROUP)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE,
              fullrange = TRUE) +
  geom_text(data = eq_pos, aes(x = x, y = y, label = label),
            hjust = 0, show.legend = FALSE) +
  scale_x_continuous(breaks = c(1, 2), limits = c(0.8, 2.2)) +
  labs(x = "ID", y = "Movement Time (s)", colour = "Group") +
  theme_classic()

p
```